\textbf{Computational Fuzzy Extractors}

### 2013-03-01 trunk/CompFuzzExt.tex
Added discussion of LWE based PRG removed conductor language

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.  These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords of an error correcting code  no sketch is necessary.

@@

Both of the lower bound results rely on the ability to ensure that \rec serves as an error-correcting codes for most points of the output distribution.  It may be possible to avoid this problem if \rec outputs 
\subsection{Defining  Computational Fuzzy Conductors}
\label{sec:unp secure sketch}
In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.  If, the error correcting algorithm outputs a new random variable, bounds do not apply.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\begin{enumerate}
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

%We now provide a definition of a robust computational sketch using unpredictability entropy:
\begin{definition}\label{def:comp secure sketch}
A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
\end{definition}
\textbf{Note:} If some efficient algorithm can take the output of $\rec$ and transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).

%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

\section{Lossless conductor based on \class{LWE}}
\label{sec:fuzzyCompExt}

In this section we describe our main construction.  The secure sketch is computed via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
Set $X_{1,..., n/2}$ be the first of $X$.		 
\item Output $X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  Finally, in \secref{sec:lossless conductor} we describe parameter settings where our construction yields a lossless secure sketch.\lnote{revise after going through the rest}.

@@

%\begin{lemma}
%\label{lem:conversion to unpredictability}
%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
%\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits} we can use the code-offset construction in \consref{cons:informal construction} and retain HILL entropy $k\log q$.  
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  Our inverter will only succeed if it can verify it has the proper $X$. Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.   If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-1)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.

@@

\subsection{Lossless Conductor}
\label{sec:lossless conductor}
We now state a setting of parameters that yields a lossless conductor.

@@

\begin{theorem}
\label{thm:lossless secure conductor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless conductor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

@@

\section{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational fuzzy conductor for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_m)$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $(m-\alpha)$-\emph{symbol fixing source} if $H_\infty(W)\geq (m - \alpha)b$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

>>>>

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then a randomness extractor.  In the next section, we show this paradigm is difficult to realize.

%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).  We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.  These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

@@

Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.  It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).  Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
\bnote{Not happy with this wording, revise}

%\subsection{Defining  Computational Fuzzy Conductors}
%\label{sec:unp secure sketch}
%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.  If, the error correcting algorithm outputs a new random variable, bounds do not apply.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%%\begin{enumerate}
%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%%\end{enumerate}
%%\end{definition}
%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:
%
%
%%We now provide a definition of a robust computational sketch using unpredictability entropy:
%\begin{definition}\label{def:comp secure sketch}
%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
%\end{definition}
%
%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

\section{Computational Fuzzy Extractor based on \class{LWE}}
\label{sec:fuzzyCompExt}

In this section we describe our main construction.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
\item Output $X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|P) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  In \secref{sec:lossless extractor} we describe parameter settings where our construction yields a lossless secure sketch.  In \secref{sec:prg based comparison} we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.\lnote{revise after going through the rest}.

@@

%\begin{lemma}
%\label{lem:conversion to unpredictability}
%Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard then  $H^{\unp}_{\epsilon', s_{sec}'}(X_{1,..., k}|\vA, \vA X+E) \geq k\log q$
%for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
%\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With Lemmas \ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, \consref{cons:informal construction} has many hardcore bits and we use these bits as our key.  
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

@@

$\mathcal{I}_t$ is an efficient inverter/recovery procedure when $t$ is small enough.  Our inverter will only succeed if it can verify it has the proper $X$. Consider a relation $R(X, (\vA, \vA X+W-W'))$ that verifies if $X$ is the point encoded in $\vA X+W-W'$.   If $n$ is large enough and if $|W-W'|_1$ is small enough, $R$ is a unique witness relation with high probability~(see \defref{def:unique witness relation}) and computable in time $O(n^3)$.
\bnote{Need to get rid of this unique witness stuff, talk about high distance with high probability.}
We consider the setting where the running time of $\mathcal{I}_t$ grows with $t$.
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\mathcal{I}_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\mathcal{I}_t$ when $t\leq d\log n (m/n-1)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance that is a unique witness relation~(except with negligible probability).  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(m/n-1)$.  Then $\mathcal{I}_t$ runs in expected time $O(n^{2d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ for all but a negligible fraction of inputs over $\vA, \vA X+W - W'$.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-1$, then $\mathcal{I}_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-1)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\mathcal{I}_t$ is significantly better than exhaustive search over these error patterns.

@@

\subsection{Lossless Computational Fuzzy Extractor}
\label{sec:lossless extractor}
We now state a setting of parameters that yields a lossless construction.

@@

\begin{theorem}
\label{thm:lossless secure conductor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+d)/d)$.  Let $W$ be uniform over $\zo^{(c+d)/d(n\log b)}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{2d+3} \log n)$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

@@

\subsection{Comparison with \prg based construction}
\label{sec:prg based comparison}
In this section we showed how to construct a computational fuzzy extractor by making the whole process ``computational''.  Alternatively, a computational fuzzy extractor could be constructed by using an information theoretic fuzzy extractor and then applying a pseudorandom generator to the output of the fuzzy extractor.  In particular, using the same hardness of approximating GAPSVP and SIVP, Applebaum et. al. use LWE to achieve a pseudorandom generator with linear stretch~\cite{applebaum2006pseudorandom}.  Namely, consider $\vA$ as a public value, they show a setting of parameters where $f_\vA(x, e) = \vA x + e$ is a pseudorandom generator with linear stretch.  Likewise, by increasing the field size in \consref{cons:informal construction}, it is possible to output a linear factor of the number of input bits~(see \secref{sec:parameter settings}).  Both techniques are able to produce a linear stretch on the entropy of the source.  The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log t)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The disadvantages of \consref{cons:informal construction} are that it supports a limited number of errors and only a uniformly distributed source.  We begin to address this second problem in the next section.
